Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-14 proposal/mprop.tex
Finish experimental design subsection

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the final list of projects
will be finalized once some tests will be run. Then, define what makes for 2 similar tickets
(maybe look at story points assigned by experienced triagers; probably we also
need to use only severe/critical ones as they will probably be fixed first
and there will not be any delay, such as waiting for the main developer to come
back from vacation) and then see how much time it took both to be completed
so that we can infer what differences did those 2 tickets have (and see if, for
example, stack traces influenced the duration of the ticket).

@@

\textbf{Independent Variables}: components of tickets - stack traces, steps
to reproduce, grammar error free description and summary, succinct/detailed 
summary, complex/light discussion in comments

>>>>

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the list of projects
will be finalized once some tests will be run, and that is because
maybe some projects will have more valuable tickets for us to analyze and
we also decided that we want to analyze multiple issue tracking systems 
(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
\citep{bugzilla}).

Then, as most issue tracking systems respond with JSON payloads through 
their REST APIs, we can easily extract components such as summary or 
description and analyze them. We have defined that the initial list of 
components that we want to inspect into three main categories:
  \begin{itemize}
    \item regular text - summary, description, story points, 
      text in comments, status (e.g. OPEN, WONTFIX, CLOSED);
    \item non-regular text (i.e. special structures) - stack traces,
      steps to reproduce;
    \item non-text - attachments in comments (e.g. images, screenshots
      when trying to show steps to reproduce).
  \end{itemize}

Extracting text from components is rather trivial, but extracting and 
analyzing non-text data such as images or non-regular text will be 
more complex.

For images, there are two very popular REST APIs that 
we can use for analysis: Google Cloud Vision \citep{vision} and 
AWS Rekognition \citep{rekognition}. When an image is sent via the API,
the servers respond with detailed information about what can be found
in the image, thus we can detect if the image was for example a 
simple screenshot or if it contained multiple screenshots that were aimed
at visually showing steps to reproduce a bug.

In terms of non-regular text, steps to reproduce are usually trivial to
retrieve (if they are not images, for which we have presented a solution
in the above paragraph), they will most probably be written as bullet
lists or a sequence of lines starting with \emph{Step [number] ...}, thus
a simple regex will probably suffice. However, for stack traces, as they
are more complex, there are no commercial or open source applications
that could help them extract them easily, thus we will compose a special
regex depending on the language of the project (e.g. Apache heavily 
uses Java, thus we can look for lines starting with java.*.*Exception ...).

In order to detect what features make for a high quality ticket, we need 
to compare two \emph{similar} tickets and then analyze their components
for differences. Thus, one of the biggest issues we will be facing is how 
can we say that two tickets are similar. We have two initial approaches
that we want to test to see which one is more efficient:
  \begin{itemize}
    \item look solely at the issue tracking system and use story points
      to detect similar tickets; one limitation of this approach is that
      either the triager is not experienced and might assign wrong story
      point values or the initial story point values are not properly
      assigned and they will be corrected during the ticket's lifecycle;
    \item look at the version control system and compare changesets for
      similar work effort; however, this approach has one limitation - 
      solely looking at source code changes might not encapsulate the
      whole effort needed to solve the task (e.g. the developers on the
      team might spend extra hours only on designing the fix).
  \end{itemize}
However, this list is not final, so if we find some other method 
while running the experiment, we shall switch to that.

Finally, having similar tickets grouped together, we can then test 
the variances in component features they possess and see which features
affected the time-to-close the most.

@@

The study has 
\textbf{Independent Variables}: components of tickets - stack traces, steps
to reproduce, grammar error free description and summary, succinct/detailed 
summary, complex/light discussion in comments
